About

### 2025-01-25 about.qmd
Only license code as CC0
This makes it less complicated to describe,
although we deviate now from our
recommendations (regarding CC0's lack of patent
grant).

Except where noted otherwise, the material in this tutorial is licensed under [CC\ BY-SA\ 4.0](https://creativecommons.org/licenses/by-sa/4.0/); the code chunks are also (at your option) available under [CC0\ 1.0](https://creativecommons.org/publicdomain/zero/1.0/).

>>>>

Except where noted otherwise, the text in this tutorial is licensed under [CC\ BY-SA\ 4.0](https://creativecommons.org/licenses/by-sa/4.0/); the code without any text is also (at your option) available under [CC0\ 1.0](https://creativecommons.org/publicdomain/zero/1.0/).
